A Reimplementation of Python’s dict using Simple Tabulation Hashing and Linear Probing

### 2012-05-20 docs/paper.tex
Add graphs

\subsection{Implementation Details}
We prepopulated random tables in memory with random bits from random.org, which sources randomness form atmospheric noise.

>>>>

\subsection{Implementation Details}
We prepopulated random tables in memory with random bits from random.org, which
sources randomness form atmospheric noise in order to remove the reliance on
pseudo-random number generators.

      Following is an excerpt from our hashing code.  We use bit tricks in
      order to prevent costly modulo instructions.  For each byte in the
      string, we construct an index by adding the byte value and a table offset
      together.  Then we lookup the value in a large table of random 64 bit
      longs and then XOR it with the previous result in the chain of XORs.
